Simple Type Theory is not too Simple

### 2021-04-07 article.tex
Updates from Overleaf

\begin{thebibliography}{}

	\bibitem{Group-Ring-Module-AFP}
	Kobayashi H., Chen L. and Murao H.:
	\newblock \textit{Groups, Rings and Modules}.
	\newblock Archive of Formal Proofs (2004)

	\bibitem{VectorSpace-AFP}
	Lee H.:
	\newblock \textit{Vector Spaces}.
	\newblock Archive of Formal Proofs (2014)

	\bibitem{ballarin2014}
	Ballarin, C.: 
	\newblock \textit{Locales: A Module System for Mathematical Theories}.
	\newblock J. Autom. Reason. 52, 123–153 (2014)

	\bibitem{ballarin20}
	Ballarin, C.:
	\newblock \textit{Exploring the Structure of an Algebra Text with Locales}. 
	\newblock J. Autom. Reason. 64(6), 1093–1121 (2020)

	\bibitem{chiclithesis}
	Chicli L.:
	\newblock \textit{Sur la formalisation des math\'ematiques dans le Calcul des Constructions Inductives}.
	\newblock doctoral thesis (2003)

	\bibitem{GrothendieckEGAI}
	Grothendieck A.:
	\newblock \textit{\'El\'ements de g\'eom\'etrie alg\'ebrique. I. Le langage des sch\'emas}.
	\newblock Inst. Hautes \'Etudes Sci. Publ. Math., no. 4, 228. MR 217083 (1960)

	\bibitem{schemesinLean}
	Buzzard K., Hughes C., Lau K., Livingston A., Mir R. and Morrison S.:
	\newblock \textit{Schemes in Lean}.
	\newblock arXiv:2101.02602

	\bibitem{hartshorne}
	Hartshorne, R.:
	\newblock \textit{Algebraic Geometry}.
	\newblock Graduate Texts in Mathematics, Springer (1977)

	\bibitem{bordg18}
	Bordg A.:
	\newblock \textit{The Localization of a Commutative Ring}.
	\newblock Archive of Formal Proofs (2018)

	\bibitem{typestosets}
	Kunčar, O., Popescu, A.:
	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
	\newblock J. Autom. Reason. 62, 237–260 (2019)

	\bibitem{PaulsonLamport}
	Lamport, L. and Paulson, L. C.:
	\newblock \textit{Should Your Specification Language Be Typed}.
	\newblock  ACM Transactions on Programming Languages and Systems (TOPLAS) 21, no. 3, 502-526 (1999)

\end{thebibliography}

>>>>

\bibliographystyle{plain}
\bibliography{ALEXANDRIA}
